Call Center Regression Data Analysis

### 2022-11-12 Manuscript/Manuscript.tex
commit #discussion
commit

\section*{Introduction}
  With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
in the United States alone, call centers play a pivotal role in a business' success. Call centers are a key part of customer service
that will save a company time, money, and unneccessary obstacles. In the banking industry, calls can range from inquires, transfers, 
payments, reporting, to processing. This means members could call about their account balance, credit card bills, loan applications, 
or unauthorized transactions. It is crucial that a bank is prepared for spikes in calls and have agents knowledgeable in all aspects of banking.

@@

I also created a tabled that shows the average wait time, talk time, hold time, wrap up time, and count of every Interaction Outcome.

@@

as most people are working throughout the day.

@@

100 seconds is the cutoff for most people that Abandoned. That could be a goal for this bank to get too, to prevent more Abandoned calls. 

@@

I used Pearson's correlation which states the following assumptions,

@@

@@

In regards to forecasting the number of agents, I create one last table to see if there is a difference in AgentHandleTime and WaitTime
by each 15 minute interval.
\begin{table}[H]
  \resizebox{\textwidth}{!} {
  \begin{tabular}{ l | l | l | l | l | l | l |}
    {\bf DayofWeek} & {\bf AvgNumCalls} & {\bf AvgNumAgents} & {\bf CallsPerAgent} & {\bf AvgAgentHandleTime} & {\bf AvgWaittime} & {\bf AvgInteractionValue}\\
  \hline
  2 & 2418 & 10.6 & 227 & 303 & 175 & 0.987 \\
  \hline
  3 & 2701 & 10.4 & 260 & 297 & 126 & 0.998\\
  \hline
  4 & 2710 & 10.7 & 254 & 297 & 80.9 & 0.987 \\
  \hline
  5 & 2573 & 10.2 & 253 & 289 & 87.1 & 0.988 \\
  \hline
  6 & 2897 & 9.93 & 292 & 293 & 88.2 & 0.987 \\
  \hline
  7 & 736 & 6.34 & 116 & 260 & 57.4 & 0.989\\
  \end{tabular}
  }
  \end{table}
Overall, we see that Friday continues to be the busiest days in terms of call volume but the least staffed days. However, a glaring note
is how high the average waittime on Monday is. This may be suggesting that the subject matter of calls on Monday are more intense and urgent
then the subject matter on a day like Saturday. With such a high wait time but not a bigger handle time, this also may be suggesting that
employees are getting stressed out at lot more and may need more time to get themselves mentality ready to take the next call. It might be a good idea to add another employee for Mondays. 
The other days appear to be relatively normal and Saturday is functioning very efficiently. With a waittime less than 60 seconds, there is no reason to change the staffing model for
Saturday.

  From there I ran Correlation between CallsPerAgent and the dependent variables. The Pearson Product Moment Correlation test can take a range of values from 1 to -1. A value of 0 shows there is no association between two variables. 
A value greater than 0 indicates a positive association, meaning as the value of the dependent variable increases so does the independent variable. A value less than 0 indicates a negative association, meaning as the dependent 
variable decreases so does the independent variable. The stronger the correlation between the variables the higher it is to 1 or -1.  The 4 dependent variables were Average Wait Time, Average Call Time, Average Goal Being Met, Average Interaction Value. 
The one dependent variable is CallsPerAgent. In this case, the Calltime is the same as Handletime, which is the combination of Wait time, Hold time, and Wrap Up Time. 
The Average Goal Being Met would be whatever the business establishes in seconds of  how long they would want a call center call to last. Average Interaction Value would be at what percentage 
they want calls being "Handled" or taken by an agent in anyway. 
\begin{table}[H]
  \resizebox{\textwidth}{!} {
  \begin{tabular}{ l | l |}
    {\bf Dependent Variable} & {\bf Correlation Coefficient}\\
  \hline
  Wait Time& 0.405 \\
  \hline
  Call Time& 0.238\\
  \hline
  Goal Met& -0.496  \\
  \hline
  Interaction Value& 0.484\\
  \end{tabular}
  }
  \end{table}
Typically, a Pearson's coefficient ranging between plus or minus .3 represents a small association, while a Pearson's coefficient
ranging between plus or minus .3 to .5 represents a medium association, and anything over plus or minus .5 represents a large association.
Wait Time and Calls Per Agent have a medium positive relationship which states as Calls Per Agent increases, so does the Wait Time for 
each Caller. Call Time and Calls Per Agent have a small positive relationship which states as Calls Per Agent increases, so does the 
Call Time. Goal Time and Calls Per Agents have the strongest relationship, in this case a negative medium relationship, which states as
Calls Per Agents increases, the Goal Being Met decreases. This means the Average Goal Time is nothing being hit consistently when Calls 
are increasing. Interaction Value and Calls Per Agent have a medium positive relationship. However, in theory, as calls increase there should
be more abandoned calls, but according to Pearsons Coefficient this is not the case. So while this relationship may not be a linear one,
I will still present a model for it.
\section*{Discussion}

>>>>

\section*{Introduction}
  With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
in the United States alone, call centers play a pivotal role in a business' success. Call centers are a key part of customer service
that will save a company time, money, and unneccessary obstacles. \citep{feinberg2002operational} claims call centers serve as a source of service recovery, added value, market intelligence, and strategic advantage
In the banking industry, calls can range from inquires, transfers, payments, reporting, to processing. This means members could call about their account balance, credit card bills, loan applications, 
or unauthorized transactions. It is crucial that a bank is prepared for spikes in calls and have agents knowledgeable in all aspects of banking and are capable of handling customer impatience. \citep{brown2005statistical}

@@

I also created a table that shows the average wait time, talk time, hold time, wrap up time, and count of every Interaction Outcome.

@@

as most people are working throughout the day. From a managers view, important to have your best employees not on break during that time so they are ready to solve 
any complications that come up. \citep{rafaeli2008impact}

@@

100 seconds is the cutoff for most people that Abandoned. That could be a goal for this bank to get too, to prevent more Abandoned calls. While 
the number itself is not significant, Avramidis explains that "The maximal time a customer is willing to wait in queue is his patience time, A, also known as time-to-abandonment. The
time he must wait before beginning service is his virtual queue time, V. The actual wait time is W = min(A,V), terminated by either abandonment (whenever V > W), or beginning of service (V = W).
In heavy traffic, even a small fraction of calls that abandon the queue can have a dramatic effect on system performance" \citep{avramidis2005modeling}. This means that just reducing seconds
in waittime could allow for a more efficient contact call system.

@@

Logistic and Linear Regression Assumptions: Violation Recognition and Control goes into detail about this stating, "it is necessary to make a note about sample size for this type of regression model. In Linear
regression the sample size rule of thumb is that the regression analysis requires at least 20 cases per
independent variable in the analysis"\citep{schreiber2018logistic} 
I also used Pearson's correlation which states the following assumptions,

@@

The Pearsons coefficient is given below:
\begin{equation}
  \label{eq:Pearson}
r= \Sigma((x_i - \bar{x})(y_i-\bar{y}))/(\sqrt{\Sigma{(x_i-\bar{x})^2}\Sigma{(y_i-\bar{y})^2}}),
\end{equation}

@@

In regards to forecasting the number of agents, I created one last table to see if there is a difference in AgentHandleTime and WaitTime
by each 15 minute interval.
\begin{table}[H]
  \resizebox{\textwidth}{!} {
  \begin{tabular}{ l | l | l | l | l | l | l |}
    {\bf DayofWeek} & {\bf AvgNumCalls} & {\bf AvgNumAgents} & {\bf CallsPerAgent} & {\bf AvgAgentHandleTime} & {\bf AvgWaittime} & {\bf AvgInteractionValue}\\
  \hline
  2 & 2418 & 10.6 & 227 & 303 & 175 & 0.987 \\
  \hline
  3 & 2701 & 10.4 & 260 & 297 & 126 & 0.998\\
  \hline
  4 & 2710 & 10.7 & 254 & 297 & 80.9 & 0.987 \\
  \hline
  5 & 2573 & 10.2 & 253 & 289 & 87.1 & 0.988 \\
  \hline
  6 & 2897 & 9.93 & 292 & 293 & 88.2 & 0.987 \\
  \hline
  7 & 736 & 6.34 & 116 & 260 & 57.4 & 0.989\\
  \end{tabular}
  }
  \end{table}
  Overall, we see that Friday continues to be the busiest days in terms of call volume but the least staffed days. However, a glaring note
is how high the average waittime on Monday is. This may be suggesting that the subject matter of calls on Monday are more intense and urgent
then the subject matter on a day like Saturday. With such a high wait time but not a bigger handle time, this also may be suggesting that
employees are getting stressed out at lot more and may need more time to get themselves mentality ready to take the next call. It might be a good idea to add another employee for Mondays. 
The other days appear to be relatively normal and Saturday is functioning very efficiently. With a waittime less than 60 seconds, there is no reason to change the staffing model for
Saturday.

  From there I ran Correlation between CallsPerAgent and the dependent variables. The Pearson Product Moment Correlation test can take a range of values from 1 to -1. A value of 0 shows there is no association between two variables. 
A value greater than 0 indicates a positive association, meaning as the value of the dependent variable increases so does the independent variable. A value less than 0 indicates a negative association, meaning as the dependent 
variable decreases so does the independent variable. The stronger the correlation between the variables the higher it is to 1 or -1.  The 4 dependent variables were Average Wait Time, Average Call Time, Average Goal Being Met, Average Interaction Value. 
The one dependent variable is CallsPerAgent. In this case, the Calltime is the same as Handletime, which is the combination of Wait time, Hold time, and Wrap Up Time. 
The Average Goal Being Met would be whatever the business establishes in seconds of  how long they would want a call center call to last. Average Interaction Value would be at what percentage 
they want calls being "Handled" or taken by an agent in anyway. 
\begin{table}[H]
  \resizebox{\textwidth}{!} {
  \begin{tabular}{ l | l |}
    {\bf Dependent Variable} & {\bf Correlation Coefficient}\\
  \hline
  Wait Time& 0.405 \\
  \hline
  Call Time& 0.238\\
  \hline
  Goal Met& -0.496  \\
  \hline
  Interaction Value& 0.484\\
  \end{tabular}
  }
  \end{table}
Typically, a Pearson's coefficient ranging between plus or minus .3 represents a small association, while a Pearson's coefficient
ranging between plus or minus .3 to .5 represents a medium association, and anything over plus or minus .5 represents a large association.
Wait Time and Calls Per Agent have a medium positive relationship which states as Calls Per Agent increases, so does the Wait Time for 
each Caller. Call Time and Calls Per Agent have a small positive relationship which states as Calls Per Agent increases, so does the 
Call Time. Goal Time and Calls Per Agents have the strongest relationship, in this case a negative medium relationship, which states as
Calls Per Agents increases, the Goal Being Met decreases. This means the Average Goal Time is nothing being hit consistently when Calls 
are increasing. Interaction Value and Calls Per Agent have a medium positive relationship. However, in theory, as calls increase there should
be more abandoned calls, but according to Pearsons Coefficient this is not the case. So while this relationship may not be a linear one,
I will still present a model for it.

  Here are the linear models:
  \begin{equation}
    \label{eq:Wait Time}
  AvgWaittime= -5.292 + 61.148*CallsPerAgent,
  \end{equation}
  \begin{equation}
    \label{eq:Call Time}
  AvgCallTime = -256.252 + 20.115*CallsPerAgent,
  \end{equation}
  \begin{equation}
    \label{eq:Goal Met}
  AvgGoalMet= 0.986 - 0.216*CallsPerAgent,
  \end{equation}
  \begin{equation}
    \label{eq:InteractionValue}
  AvgInteractionValue= 0.97 + 0.00989*CallsPerAgent,
  \end{equation}

  \begin{table}[H]
    \resizebox{\textwidth}{!} {
    \begin{tabular}{ l | l |}
      {\bf Dependent Variable} & {\bf R-squared Value}\\
    \hline
    Wait Time& 0.1642 \\
    \hline
    Call Time& 0.0569\\
    \hline
    Goal Met& 0.2458\\
    \hline
    Interaction Value& 0.234\\
    \end{tabular}
    }
    \end{table}
R-squared values range from 0 to 1. A R-squared value of 1 means that all movements of a variable are completely explained by another variable. 
Overall, the higher the R-squared the better.
\section*{Discussion}
Overall, the best agent model would be the model with the highest R-squared value and Pearson Coefficient. In this case, this would be
AvgGoalMet= 0.986 - 0.216*CallsPerAgent. A close second place would be AvgWaittime= -5.292 + 61.148*CallsPerAgent, as it had a decent 
Pearson coefficient and R-squared value. Unfortunately, because of the Pearsons Coefficient I would not recommend the Interaction Value model however even though it had a good 
r-squared value. Overall the other 3 models are would suggest to an individual to use to determine how many agents
there business to have. Unfortunately, there are so many aspects to just this. In regards to a business perspective, the call center must have
a budget so it is a difficult road to navigate. But, I believe it is possible to find a balance in between to ultimately maximize efficiency.
We were also able to forecast call center volume using historical data and the ratio of how many hours the call center is open compared to each day to
a week.

  The biggest limitation I would say was that there is no right answer to answering the calls per agent problem. In an ideal situation, you would have
plenty of agents so waittime is completely reduced. However that is not efficient or plausible. I also do wish I knew the answer to what
the actual Goal time was, this would help me be more confident in my model I created. I did try to create a model to the ratio of Calls Per Agent,
but Unfortunately the parameters estimates were simply just inaccurate.

Another challenge was dealing with the time complexities in the dataset. There are 6 days of the week, 47 15-minute-intervals across any day, which each occur a different number of times,
and 213 15-minute-intervals across each week. This does not average out between days of the week. There was also 139 weeks in the data, 971 days in all the data, and
27377 15-minute-intervals in all the data. So this fails to account for discrepancies in between days of the week. Also, Call time and any values
about the all are data explicitly about the call so they are in the row in the itself, so we have to normalize the number of agents by number of calls During
that period recorded before we run a model comparing both values. So overall, there was a lot of data cleaning and preparing needed in this dataset, that
took time away from the data analysis.

  I still believe this study can be expanded on. Monday has a wait time of 175 seconds while Friday has a wait time of 88.2 seconds. Possibly multivariate regression technqiues could be used to model the number of agents needed.
With the data at my hands, I could also try to answer questions such as if call length is dependenton call reason or even do an analysis on if all agents are performing
on the same level. In detail, \citep{evensen1999effective} believes that "Since the primary interface between a financial institution and its customer is a service
representative, this element strongly influences an institution's ability to deliver quality service.An organization’s human resource (HR) practices effect how well its employees are able to perform. More
specifically, human resource practices directly influence how knowledgeable an employee is about the product offering, whether or not an employee is empowered to resolve customer issues in real time, and the
level of turnover within the organization". This is an interesting point as one could analyze how Human Resources Data plays a role in qualities like AgentHandleTime that reflects on the agents performance. Another interesting question to look into was the abandonment 
rate and if how many times someone will call back the same day. I personally did not look into the chat feature that much, but I am sure that there is some interesting information like if people tend to reuse often.
Another topic of interest is how does call center volume change on when there is an information technology problem such as the online banking services having an outage?
